MINOS Handover Plots

### 2023-05-02 minos/validation/handovers.Rmd
Changed the utils script to separate out the datain utilities (now in own script). Also changed some function names in the new utils_datain script to be more obvious as to their purpose (some docstring style stuff in there too). Added a new script for testing out some new outcomes visualisations, in standard_deviation_change_SF12.Rmd. More to come
Added a save.path variable to handovers.Rmd, and added some calls to ggsave to save figures for adding to the overleaf paper. Also specified dplyr::select for the select functions as a different package was masking the select function

```{r}
start.year <- 2020
```

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income)) %>%
  mutate(source = 'baseline_output')

@@

raw.income2 <- raw.dat %>% 
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.income2 <- base.dat %>%
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Household Income', subtitle = 'Wave 1 Sample') +
  xlab('Year') +
  ylab('Income')

raw.income.check <- raw.dat %>% 
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

base.income.check <- base.dat %>%
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.sf12.2 <- raw.dat %>% 
  select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Wave 1 Sample') +
  xlab('Year') +
  ylab('SF12')
```

@@

```{r}
raw.housing <- raw.dat %>% 
  select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'final_US')

base.housing <- base.dat %>%
  select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Proportion') +
  xlab('Year') +
  ylab('Proportion')

@@

```{r}
raw.neighbour <- raw.dat %>% 
  select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Proportion') +
  xlab('Year') +
  ylab('Proportion')

@@

```{r}
raw.loneliness <- raw.dat %>% 
  select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Loneliness', subtitle = 'Proportion') +
  xlab('Year') +
  ylab('Proportion')

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nut <- raw.dat %>% 
  select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut <- base.dat %>%
  select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.nut2 <- raw.dat %>% 
  select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  filter(nutrition_quality >= 0) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut2 <- base.dat %>%
  select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Nutrition Quality', subtitle = 'Wave 1 Sample') +
  xlab('Year') +
  ylab('Nutrition Quality')

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.phealth2 <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health', subtitle = 'Wave 1 Sample') +
  xlab('Year') +
  ylab('Average')

>>>>

```{r}
start.year <- 2020

save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Handovers/'
```

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  dplyr::select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income)) %>%
  mutate(source = 'baseline_output')

@@

raw.income2 <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.income2 <- base.dat %>%
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Household Income') +
  xlab('Year') +
  ylab('Income')

ggsave(filename = 'hh_income_wav1.png',
       plot = last_plot(),
       path = save.path)

raw.income.check <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

base.income.check <- base.dat %>%
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.sf12.2 <- raw.dat %>% 
  dplyr::select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Mental Wellbeing (SF12 MCS)') +
  xlab('Year') +
  ylab('SF12')

ggsave(filename = 'SF12_wav1.png',
       plot = last_plot(),
       path = save.path)
```

@@

```{r}
raw.housing <- raw.dat %>% 
  dplyr::select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'final_US')

base.housing <- base.dat %>%
  dplyr::select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'housing_quality.png',
       plot = last_plot(),
       path = save.path)

@@

```{r}
raw.neighbour <- raw.dat %>% 
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Neighbourhood Safety') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'neighbourhood_safety.png',
       plot = last_plot(),
       path = save.path)

@@

```{r}
raw.loneliness <- raw.dat %>% 
  dplyr::select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  dplyr::select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')

@@

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Loneliness') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'loneliness.png',
       plot = last_plot(),
       path = save.path)

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nut <- raw.dat %>% 
  dplyr::select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut <- base.dat %>%
  dplyr::select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.nut2 <- raw.dat %>% 
  dplyr::select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  filter(nutrition_quality >= 0) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut2 <- base.dat %>%
  dplyr::select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Nutrition Quality') +
  xlab('Year') +
  ylab('Nutrition Quality')

ggsave(filename = 'nutrition_quality_wav1.png',
       plot = last_plot(),
       path = save.path)

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.phealth2 <- raw.dat %>% 
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health') +
  xlab('Year') +
  ylab('Average')

ggsave(filename = 'physical_health_wav1.png',
       plot = last_plot(),
       path = save.path)
